---
title: 'MISSOURI Primary and Secondary Analysis Results'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE,warning=FALSE)
```

```{r Required_Packages}
library(RODBC)
library(tcltk)
library(xlsx)
library(SCCS)
library(lubridate)
library(tidyr)
library(kableExtra)
library(ggplot2)
 theme_set(theme_bw())#sets theme for plots - white background
```

```{r Connect}
# connect to SAIL SQL
getLogin<-function(userName=''){  
  require(tcltk);  
  wnd<-tktoplevel();
  tclVar(userName)->user;
  tclVar("")->passVar;
  #Label  
  
  #Username box  
  tkgrid(tklabel(wnd,text="Username:"));  
  tkgrid(tkentry(wnd,textvariable=user)->passBox);  
  
  #Password box  
  tkgrid(tklabel(wnd,text="Password:"));  
  tkgrid(tkentry(wnd,textvariable=passVar,show="*")->passBox);  
  #Hitting return will also submit password  
  tkbind(passBox,"<Return>",function() tkdestroy(wnd));  
  #OK button  
  tkgrid(tkbutton(wnd,text="OK",command=function() tkdestroy(wnd)));  
  #Wait for user to click OK  
  tkwait.window(wnd);  
  password<-tclvalue(passVar);
  userName<-tclvalue(user);
  return(c(userName,password));  
} 

login <- getLogin('reeven') # change user name and provide SAIL password in pop up box 
channel <- odbcConnect('PR_SAIL',login[1],login[2]) # connect to DB2/SAIL 
rm(login) # hides password 
```

```{r ReadData}

#primary
#stroke
PriStroke<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_STROKE_PRIMARY")
PriStroke$UTI_DT<-PriStroke$DIAG_DT
#MI
PriMI<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_MI_PRIMARY")
PriMI$UTI_DT<-PriMI$DIAG_DT

#secondary 1
#stroke
Sec1Stroke<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_STROKE_SECANAL1")
Sec1Stroke$UTI_DT<-Sec1Stroke$DIAG_DT
#MI
Sec1MI<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_MI_SECANAL1")
Sec1MI$UTI_DT<-Sec1MI$DIAG_DT

#secondary 2
#stroke
Sec2Stroke<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_STROKE_SECANAL2")
#MI
Sec2MI<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_MI_SECANAL2")

#secondary 3
#stroke
Sec3Stroke<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_STROKE_SECANAL3")
Sec3Stroke$UTI_DT<-Sec3Stroke$DIAG_DT
#MI
Sec3MI<- sqlQuery(channel, "SELECT * FROM SAILW0972V.V2_VB_MI_SECANAL3")
Sec3MI$UTI_DT<-Sec3MI$DIAG_DT


```

```{r AnalysisFunc}

analysis<-function(CVE){

#prepare for analysis
  
#calculate required variables
#calculate age at event
CVE$Age_Event<-as.numeric(CVE$FIRST_EVENT_DT-CVE$WOB)
#calculate age at UTI
CVE$UTI<-as.numeric(CVE$UTI_DT-CVE$WOB)
#calculate age at start of obs
CVE$Age_Obs_Start<-as.numeric(CVE$INC_START-CVE$WOB)
#calculate age at end of obs
CVE$Age_Obs_End<-as.numeric(CVE$INC_END-CVE$WOB)
#Extract year from event date
CVE$Event_Year<-year(CVE$FIRST_EVENT_DT)
#WOB in required format
CVE$WOBdmy<- as.numeric(paste(format.Date(CVE$WOB, "%d"),format.Date(CVE$WOB, "%m"), year(CVE$WOB),sep=""))
#age at 2010, for adjusting for year - allows the model to see where the event is in relation to 2010 - first 365 days, second, third etc
CVE$age2010<-as.numeric(as.Date("2010-01-01")-CVE$WOB)
#if use stack - individuals with multiple UTIs should have NA in all but first row of age2010. (#doesn't actually make a difference)
CVE$age2010[duplicated(CVE$ALF_PE)]<-NA
 
#calculate age quartiles 
age_at_event_q<-floor(quantile(CVE$Age_Event[duplicated(CVE$ALF_PE)==0],seq(0.025,0.975,0.025),names=F)) 
  
#run main model - age, season and year adjusted
CVE.Year<-standardsccs(event~UTI+age2010+relevel(age,ref=21)+season,
                         indiv=ALF_PE, astart=Age_Obs_Start, 
                       aend=Age_Obs_End, 
                       aevent=Age_Event,adrug=cbind(UTI,age2010),
                       aedrug=cbind(UTI+90,age2010+4018),
                  expogrp=list(c(-7,0,8,15,29),c(0,365,730,1096,1461,1826,2191,2557,2922,3287,3652)), agegrp=age_at_event_q,
                         seasongrp=c(0101,0104,0107,0110), dob=WOBdmy,
                         dataformat = "stack",data=CVE)

#crude model
CVE.crude<-standardsccs(event~UTI,
                         indiv=ALF_PE, astart=Age_Obs_Start, 
                       aend=Age_Obs_End, 
                       aevent=Age_Event,adrug=UTI,
                       aedrug=UTI+90,
                  expogrp=c(-7,0,8,15,29),
                         dataformat = "stack",data=CVE)

#age adjusted
CVE.age<-standardsccs(event~UTI+relevel(age,ref=21),
                         indiv=ALF_PE, astart=Age_Obs_Start, 
                       aend=Age_Obs_End, 
                       aevent=Age_Event,adrug=UTI,
                       aedrug=UTI+90,
                  expogrp=c(-7,0,8,15,29), agegrp=age_at_event_q,
                          dataformat = "stack",data=CVE)

# ##############################

#collate results into result table

#tables of coefficients
#crude
CrudeTab<-CVE.crude$conf.int[1:5,]
#coefficients and confidence intervals
CrudeTab<-paste(round(CrudeTab[,1],2), " (", round(CrudeTab[,3],2), " - ", round(CrudeTab[,4],2),")",sep="")

#age adjusted
AgeTab<-CVE.age$conf.int[1:5,]
#coefficients and confidence intervals
AgeTab<-paste(round(AgeTab[,1],2), " (", round(AgeTab[,3],2), " - ", round(AgeTab[,4],2),")",sep="")

#main - age, season, year adjusted
YearTab<-CVE.Year$conf.int[1:5,]
#coefficients and confidence intervals
YearTab<-paste(round(YearTab[,1],2), " (", round(YearTab[,3],2), " - ", round(YearTab[,4],2),")",sep="")

#calculate total observation time and n events
#days
CVE_format<-formatdata(indiv=ALF_PE, astart=Age_Obs_Start, 
                       aend=Age_Obs_End, 
                       aevent=Age_Event,adrug=UTI,
                       aedrug=UTI+90,
                  expogrp=c(-7,0,8,15,29),
                         dataformat = "stack",data=CVE)
timeTab<-aggregate(CVE_format$interval,by=list(RiskPeriod=CVE_format$UTI),FUN=sum, drop=FALSE)
NEventTab<-aggregate(CVE_format$event,by=list(RiskPeriod=CVE_format$UTI),FUN=sum, drop=FALSE)
times<-timeTab[,2]
Nevents<-NEventTab[,2]

ResTab<-matrix(c("Baseline","Pre-Risk", "0-7 days", "8-14 days", "15-28 days", "29-90 days", 
                 round(Nevents,-1),
                 times,
                 1,CrudeTab,
                 1, AgeTab,
                 1,YearTab),nrow=6)

ResTab<-data.frame(ResTab)
colnames(ResTab)<-c("Time period", 
                    "No Events",
                    "Total Obs Time (days)", "Crude IRR (95% CI)", "Age Adjusted IRR (95% CI)", "Age, Season and Year adjusted IRR (95% CI)")

ResTab$`Total Obs Time (days)`[ResTab$`No Events`==0]<- round(as.numeric(ResTab$`Total Obs Time (days)`[ResTab$`No Events`==0]),-2)

#plot using ggplot2
fig<-ggplot(mapping=aes(x=c(-7,-1, 0,7, 8,14, 15,28, 29,90), y=rep(CVE.Year$conf.int[1:5,1],each=2)))+
  geom_step()+
  geom_hline(yintercept=1, size=0.4, linetype="dashed")+
  xlab("Days Since UTI")+ylab("Relative Incidence")+
  ylim(0,5.2)


return(list(ResTab,fig))
}

```

```{r ResultsFunc}

results<-function(ResMI, ResStroke){
  
#MI
ResMI_kbl<-kbl(ResMI[[1]],caption="MI")
MIkbl<-kable_styling(kable_input= ResMI_kbl, full_width = F, position = "left", font_size = 12)
#plot
MIplot<-ResMI[[2]]+ labs(title="MI")

#stroke
ResStroke_kbl<-kbl(ResStroke[[1]],caption="Stroke")
Strokekbl<-kable_styling(kable_input= ResStroke_kbl, full_width = F, position = "left", font_size = 12)
#plot
Strokeplot<-ResStroke[[2]]+ labs(title="Stroke")

return(list(MIkbl,MIplot,Strokekbl,Strokeplot))

}

```

# Introduction

This document presents results of the self-controlled case series analysis of acute cardiovascular events (MI and stroke), with UTI as exposure. 
Number of events are all rounded to the nearest ten. When number of events is <=5, number of events is assigned 0, and total observation time is rounded to the nearest 100.

# Data

Data Tables:  SAILW0972V.V2_VB_STROKE_PRIMARY, SAILW0972V.V2_VB_MI_PRIMARY,
              SAILW0972V.V2_VB_STROKE_SECANAL1, SAILW0972V.V2_VB_MI_SECANAL1,
              SAILW0972V.V2_VB_STROKE_SECANAL2, SAILW0972V.V2_VB_MI_SECANAL2,
                            SAILW0972V.V2_VB_STROKE_SECANAL3, SAILW0972V.V2_VB_MI_SECANAL3
              
PEDW Cohort specification is as follows:

- Main Dataset: Patient Episode Database for Wales (PEDW)
- Date range: 2010-01-01 to 2020-12-31
- Data cleanse: only records with non-null ALFs with a matching status of 1,4 or 39 are included 
- Only episodes with a finished episode flag are included
- Age inclusion: Between 30 and 100 (inclusive) at date of event
- Geographical inclusion: Welsh resident at date of event
- Diagnosis inclusion based on agreed ICD-10 codes
- Event inclusion: First MI and Stroke event for individual within the date range when all other inclusion criteria are met

Of those in the above cohort, include only those who have the agreed UTI and antibiotic Read codes in WLGP, and a urine culture result as appropriate for each definition of UTI.


# Primary Analysis

For the primary analysis, the definition of UTI is: a UTI-related Read code in WLGP data, an antibiotic prescription, and a positive urine culture, occurring within a 7-day window.

```{r PriAnalysis}
PriMIRes<-analysis(PriMI)
PriStrokeRes<-analysis(PriStroke)

PriRes<-results(PriMIRes,PriStrokeRes)
PriRes[[1]]
PriRes[[2]]
PriRes[[3]]
PriRes[[4]]

```


# Secondary Analysis 1

For secondary analysis 1, the definition of UTI is: a UTI-related Read code in WLGP data, an antibiotic prescription, and a positive urine culture with mixed growth, occurring within a 7-day window.


```{r Sec1Analysis}

Sec1MIRes<-analysis(Sec1MI)
Sec1StrokeRes<-analysis(Sec1Stroke)


Sec1Res<-results(Sec1MIRes,Sec1StrokeRes)
Sec1Res[[1]]
Sec1Res[[2]]
Sec1Res[[3]]
Sec1Res[[4]]
```

# Secondary Analysis 2

For secondary analysis 2, the definition of UTI is: a UTI-related Read code in WLGP data and an antibiotic prescription, occurring within a 7-day window.

```{r Sec2Analysis}

Sec2MIRes<-analysis(Sec2MI)
Sec2StrokeRes<-analysis(Sec2Stroke)

Sec2Res<-results(Sec2MIRes,Sec2StrokeRes)
Sec2Res[[1]]
Sec2Res[[2]]
Sec2Res[[3]]
Sec2Res[[4]]
```

# Secondary Analysis 3

For secondary analysis 3, the definition of UTI is: a UTI-related Read code in WLGP data, an antibiotic prescription, and a negative urine culture, occurring within a 7-day window.

```{r sec3Analysis}

Sec3MIRes<-analysis(Sec3MI)
Sec3StrokeRes<-analysis(Sec3Stroke)

Sec3Res<-results(Sec3MIRes,Sec3StrokeRes)
Sec3Res[[1]]
Sec3Res[[2]]
Sec3Res[[3]]
Sec3Res[[4]]
```
